### 2014-04-29 docs/seminar/evaluation.tex
more changes
more changes
still to do: fit it to 12 pages, re-write conclusion

\begin{figure}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.8\textwidth]{figures/aggregation_plots_gp2.png}
	\caption{GP2}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.8\textwidth]{figures/aggregation_plots_top5.png}
	\caption{TOP5}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.8\textwidth]{figures/aggregation_plots_top1.png}
	\caption{TOP1}
\end{subfigure}
\caption{Data distribution of aggregation values against proof-readers' assessments. Axes X shows the assessments of proof-readers. axes Y represents the values of the corresponding aggregation function}
\label{fig:aggregationplot}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{c c|c|c|c|}
\cline{3-5} & & Top1 & Top5 & GP2  \\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$r_s$}} & Correlation Test & 0.052 & 0.089 & 0.145\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.4866 & 0.2295 & 0.05038\\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$\tau$}} & Correlation Test & 0.034 & 0.059 & 0.102\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.5157 & 0.2562 & 0.05263\\
\hline
\end{tabular}
\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
\label{table:correlation}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline \multirow{2}{*}{Method} & \multicolumn{2}{ c| }{NDCG@3} & \multicolumn{2}{ c| }{ERR@3}  \\
\cline{2-5} & Result & Random & Result & Random \\
\hline Linear Regression & \textbf{0.935} & 0.833 & \textbf{0.451} & 0.375 \\
\hline RankNet & 0.876 & 0.834 & 0.394 & 0.378 \\
\hline RankBoost & 0.909 & 0.831 & 0.432 & 0.374 \\
\hline LambdaMART & 0.93 & 0.832 & 0.447 & 0.373 \\
\hline ListNet & 0.915 & 0.831 & 0.439 & 0.375 \\
\hline AdaRank & 0.857 & 0.83 & 0.399 & 0.373 \\
\hline Random Ranker & 0.832 & 0.832 & 0.375 & 0.378 \\
\hline
\end{tabular}
\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
\label{table:l2rresult}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|}
\hline Feature & Value  \\
\hline Price & 2.002 \\
\hline Duration & 0.057 \\
\hline Proficiency & -0.048 \\
\hline Number of Cooperation Times & -0.313 \\
\hline
\end{tabular}
\caption{Coefficient value of features in Linear Regression model}
\label{table:l2rcoefficient}
\end{table}

>>>>

\begin{figure}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.99\textwidth]{figures/aggregation_plots_gp2.png}
	\caption{GP2}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.99\textwidth]{figures/aggregation_plots_top5.png}
	\caption{TOP5}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
	\includegraphics[width=0.99\textwidth]{figures/aggregation_plots_top1.png}
	\caption{TOP1}
\end{subfigure}
\vspace{-0.3cm}
\caption{Data distribution of aggregation values against proof-readers' assessments. Axes X shows the assessments of proof-readers. axes Y represents the values of the corresponding aggregation function}
\label{fig:aggregationplot}
\vspace{-0.3cm}
\end{figure}

@@

\begin{table}
\vspace{-0.3cm}
\centering
\begin{tabular}{c c|c|c|c|}
\cline{3-5} & & Top1 & Top5 & GP2  \\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$r_s$}} & Correlation Test & 0.052 & 0.089 & 0.145\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.4866 & 0.2295 & 0.05038\\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$\tau$}} & Correlation Test & 0.034 & 0.059 & 0.102\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.5157 & 0.2562 & 0.05263\\
\hline
\end{tabular}
\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
\label{table:correlation}
\end{table}

@@

\begin{table}
\vspace{-0.3cm}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline \multirow{2}{*}{Method} & \multicolumn{2}{ c| }{NDCG@3} & \multicolumn{2}{ c| }{ERR@3}  \\
\cline{2-5} & Result & Random & Result & Random \\
\hline Linear Regression & \textbf{0.935} & 0.833 & \textbf{0.451} & 0.375 \\
\hline RankNet & 0.876 & 0.834 & 0.394 & 0.378 \\
\hline RankBoost & 0.909 & 0.831 & 0.432 & 0.374 \\
\hline LambdaMART & 0.93 & 0.832 & 0.447 & 0.373 \\
\hline ListNet & 0.915 & 0.831 & 0.439 & 0.375 \\
\hline AdaRank & 0.857 & 0.83 & 0.399 & 0.373 \\
\hline Random Ranker & 0.832 & 0.832 & 0.375 & 0.378 \\
\hline
\end{tabular}
\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
\label{table:l2rresult}
\end{table}

@@

\begin{table}
\vspace{-0.3cm}
\centering
\begin{tabular}{|c|c|}
\hline Feature & Value  \\
\hline Price & 2.002 \\
\hline Duration & 0.057 \\
\hline Proficiency & -0.048 \\
\hline Number of Cooperation Times & -0.313 \\
\hline
\end{tabular}
\caption{Coefficient value of features in Linear Regression model}
\label{table:l2rcoefficient}
\end{table}
